---
title: "Shiny Application and Reproducible Pitch"
author: "NicolasGarcesR"
date: "10/27/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Preview

This is the Developing Data Products course project.The shiny product can be found in this link <https://nicolasgarces.shinyapps.io/Course_Project_NicolasGarces/>.

The complete documentation can be found in this link <  >.

## Product

In this shiny product i made an interactive regression of the mtcars database.

the graphs shows the regression of Miles per Gallon and Wt, depending on the selected range of both variables.

when both sliders are completely to the right, you will see the regression  of the full mtcars dataset of both variables.

## Dataset

```{r cars, echo = TRUE}
summary(mtcars)
```

## Plot with full dataset (sliders to the rigth)

```{r pressure}
data1= mtcars
plot(data1$mpg, data1$wt,col="blue" ,xlim =c(9,34), ylim =c(0,6), ylab= "WT", xlab = "MPG")
abline(lsfit(data1$mpg,data1$wt),col="red")
```

